How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2014-03-07 doc/turtle_paper.Rnw
improved some tables in paper

\begin{table}
  \centering
<<results = 'asis'>>=
print.xtable(lda.tabx,
             hline.after = c(0, nrow(rf.tabx)),
             includ.rownames = TRUE,
             floating = FALSE)
@
  \caption{Results from pairwise Mann-Whitney U test between the AUC distributions of the generalizations of the LDA-based classification from the first 10 PCs of plastral shape. Labels correspond to those in Figure \ref{fig:gen_res}. Values of 0 correspond to p-values lower than 0.01. P-values were corrected for multiple comparison using the Holm method \citep{Holm1979}.}
  \label{tab:lda_test}
\end{table}

\begin{table}
  \centering
<<results = 'asis'>>=
print.xtable(mm.tabx,
             hline.after = c(0, nrow(mm.tabx)),
             includ.rownames = TRUE,
             floating = FALSE)
@
  \caption{Results from pairwise Mann-Whitney U test between the AUC distributions of the generalizations of the multinomial logistic regression models. Labels correspond to those in Figure \ref{fig:gen_res}. Values of 0 correspond to p-values lower than 0.01. P-values were corrected for multiple comparison using the Holm method \citep{Holm1979}.}
  \label{tab:mm_test}
\end{table}

\begin{table}
  \centering
<<results = 'asis'>>=
print.xtable(rf.tabx,
             hline.after = c(0, nrow(rf.tabx)),
             includ.rownames = TRUE,
             floating = FALSE)
@
  \caption{Results from pairwise Mann-Whitney U test between the AUC distributions of the generalizations of the random forest models. Labels correspond to those in Figure \ref{fig:gen_res}. Values of 0 correspond to p-values lower than 0.01. P-values were corrected for multiple comparison using the Holm method \citep{Holm1979}.}
  \label{tab:rf_test}
\end{table}

>>>>

\begin{table}
  \centering
  \include{lda_tabx}
  \caption{Results from pairwise Mann-Whitney U test between the AUC distributions of the generalizations of the LDA-based classification from the first 10 PCs of plastral shape. Labels correspond to those in Figure \ref{fig:gen_res}. Values of 0 correspond to p-values lower than 0.01. P-values were corrected for multiple comparison using the Holm method \citep{Holm1979}.}
  \label{tab:lda_test}
\end{table}

\begin{table}
  \centering
  \include{mm_tabx}
  \caption{Results from pairwise Mann-Whitney U test between the AUC distributions of the generalizations of the multinomial logistic regression models. Labels correspond to those in Figure \ref{fig:gen_res}. Values of 0 correspond to p-values lower than 0.01. P-values were corrected for multiple comparison using the Holm method \citep{Holm1979}.}
  \label{tab:mm_test}
\end{table}

\begin{table}
  \centering
  \include{rf_tabx}
  \caption{Results from pairwise Mann-Whitney U test between the AUC distributions of the generalizations of the random forest models. Labels correspond to those in Figure \ref{fig:gen_res}. Values of 0 correspond to p-values lower than 0.01. P-values were corrected for multiple comparison using the Holm method \citep{Holm1979}.}
  \label{tab:rf_test}
\end{table}
